Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
Updated paper structure

There is some domain in which requires probabilistic planning. As FF-Replan and
RFF are about using deterministic planners in a probabilistic domain, we like
to see what's new and if we can find some holes that are still open.

\section{Related Work}

@@

@@

\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

@@

From the related literature we identify some problems.

@@

\begin{itemize}
	\item Show results for the experiment
	\item Critically analyze the results
	\item Compare with results from the original papers
\end{itemize}

>>>>

We will focus on 2 of the current state of the art probablistic planning algorithms that apply determinization
in probabilistic domains and critize the approaches by formulating a real-world domain as opposed to the IPPC domains.
By comparing both approaches and analyzing other state of the art work we will propose some adjustments which we will 
theoretically test in this domain. If it is realistic, we will also try to create an emphirical evaluation.

@@

\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

@@

@@

@@

\begin{itemize}
	\item Describe the experiment setup
	\item Show results for the experiment
	\item Critically analyze the results
	\item Compare with results from the original papers
\end{itemize}
